High-Performance Primitives for Distributed Memory Architectures using Asynchronous Events

### 2012-11-14 doc/llr-pldi2013/interface.tex
minor edits for the last part of the low level paper

\begin{figure}
\begin{lrbox}{\mylistingbox}
\begin{lstlisting}
void lock_example(const void *args, size_t arglen, Processor p) {
  // Unpack lock, input events, target processors from arguments
  Lock mutex = ...
  // Acquire lock, launch first subtask, release lock
  Event lock_event_1 = mutex.lock(prev_event_1);
  Event task_event_1 = proc1.spawn(SUB, args_1, sizeof(args_1), lock_event_1);
  mutex.unlock(task_event_1);
  // same for second subtask
  Event lock_event_2 = mutex.lock(prev_event_2);
  Event task_event_2 = proc2.spawn(SUB, args_2, sizeof(args_2), lock_event_2);
  mutex.unlock(task_event_2);
}
\end{lstlisting}
\end{lrbox}
\subfigure{\usebox{\mylistingbox}}\\

@@

An important difference between deferred locks and blocking locks is that the processor
that requests the lock doesn't have to be the one that uses it.  A common
convention in writing code with deferred locks is to acquire locks on behalf of a task being
launched.  Figure~\ref{fig:lockevents} illustrates this with a simple example.  The {\tt lock\_example}
function needs to launch two subtasks on two other processors, each with exclusive access to some resource protected by a
lock named {\tt mutex}.  For each subtask, it first requests the lock on the subtask's behalf.  Using the
event returned by the lock request as a precondition, it then spawns the subtask.  The runtime will guarantee
that the subtask is not started until the lock has been acquired.  The parent task also requests that the
runtime automatically release the lock after each subtask has completed by using the subtask's completion
event as a precondition for the unlock.  In the event dependency graph (Figure~\ref{fig:lockevents}),
solid arrows represent
the explicit events used in the code, while the dotted line represents the dynamic ordering that results
from the mutual exclusion guarantee of the lock.  (In this example, the second subtask is granted the lock first.)

>>>>

\begin{figure}
\begin{lrbox}{\mylistingbox}
\begin{lstlisting}
void lock_example(const void *args, size_t arglen, Processor p) {
  // Unpack lock, input events, target processors from arguments
  Lock mutex = Lock::create_lock(); 
  // Acquire lock, launch first subtask, release lock
  Event lock_event_1 = mutex.lock(prev_event_1);
  Event task_event_1 = proc1.spawn(SUB, args_1, sizeof(args_1), lock_event_1);
  mutex.unlock(task_event_1);
  // same for second subtask
  Event lock_event_2 = mutex.lock(prev_event_2);
  Event task_event_2 = proc2.spawn(SUB, args_2, sizeof(args_2), lock_event_2);
  mutex.unlock(task_event_2);
}
\end{lstlisting}
\end{lrbox}
\subfigure{\usebox{\mylistingbox}}\\

@@

An important difference between deferred locks and blocking locks is that the processor
that requests the lock doesn't have to be the one that uses it.  A common
convention in writing code with deferred locks is to acquire locks on behalf of a task being
launched.  Figure~\ref{fig:lockevents} illustrates this with a simple example.  The {\tt lock\_example}
function needs to launch two subtasks on two other processors, each with exclusive access to some resource protected by a
lock named {\tt mutex} (created on line 3).  For each subtask, it first requests the lock on the subtask's behalf.  Using the
event returned by the lock request as a precondition, it then spawns the subtask.  The event dependence guarantees that the runtime will 
not start the subtask until the lock has been acquired.  The parent task also requests that the
runtime automatically release the lock after each subtask has completed by using the subtask's completion
event as a precondition for the unlock.  In the event dependency graph (Figure~\ref{fig:lockevents}),
solid arrows represent
the explicit events used in the code, while the dotted line represents the dynamic ordering that results
from the mutual exclusion guarantee of the lock.  (In this example, the second subtask is granted the lock first.)
